The dictionary for characters of smooth group schemes

### 2016-04-07 followup.tex
Still working on the introduction.

In Section~\ref{sec:types} we give an application of Theorem~\ref{thm:geo} by geometrizing types for supercuspidal representations of $p$-adic groups. Specifically, we show that if $C$ is a compact $p$-adic group and $\rho$ is a representation of $C$ and $(C,\rho)$ is a type for a tamely ramified $p$-adic group then there is a  group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a virtual Weil sheaf $\mathcal{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
As preparation for the proof of this statement, we review types (Section~\ref{ssec:review}) and smooth integral models (Section~\ref{ssec:models}), both as developed by Yu.  
We also review some facts about the Heisenberg-Weil representation and its geometrization (Section~\ref{ssec:Jacobi}).
These elements are pulled together in Section~\ref{ssec:geotypes}, where the proof Theorem~\ref{thm:geotypes}.

>>>>

In Section~\ref{sec:types} we give an application of Theorem~\ref{thm:geo} by geometrizing types for supercuspidal representations of $p$-adic groups. The proof of this statement, which is made precise in Theorem~\ref{thm:geotypes}, is given in Section~\ref{ssec:geotypes}. 
 %Specifically, we show that if $C$ is a compact $p$-adic group and $\rho$ is a representation of $C$ and $(C,\rho)$ is a type for a tamely ramified $p$-adic group then there is a  group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a virtual Weil sheaf $\mathcal{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
As preparation for the proof, we review some facts about the Heisenberg-Weil representation and its geometrization, in Section~\ref{ssec:Jacobi}.
Then, in Section~\ref{ssec:review}, we review Yu's theory of types and his study of smooth integral models, in Section~\ref{ssec:models}.  
These elements are pulled together in Section~\ref{ssec:geotypes}, where the proof Theorem~\ref{thm:geotypes} is given.
